---
title: "P1 Neuron Analysis"
author: "Gregory Jefferis"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

This vignette provides some quick sample analysis of P1 neurons, making use of 
the data in this package and functionality from the nat.* series of packages.

```{r startup}
library(nat)
library(p1neurons)
library(knitr)
```

## Data summary

There are `r length(p1dps)` neurons. The following metdata are available:

```{r}
kable(head(p1dps))
```

## cluster all neurons

```{r, warning=FALSE, message=FALSE}
hc=hclustfc(names(p1s))
# convert hclust to dendrogram enabling colouring/labelling
library(dendroextras)
hcd=colour_clusters(hc, k=2)
# change the labels from neuron id to sex
labels(hcd)=with(p1s[labels(hcd)], sex)
plot(hcd)
```

### Plot clusters in 3D
plot neurons in 3D broken into the 2 groups from the initial clustering
```{r,}
nopen3d()
plot3d(hc, k=2)
```


Now just keep group 2 neurons, the male-specific P1 neurons and recluster.
Cut the new clustering at a height
of h=1, which generally seems to be close to the definition of neuron type in 
other contexts.

```{r}
p1.hc=hclustfc(subset(hc, k=2, group=2))
plot(p1.hc)
clear3d()
table(slice(p1.hc, h=1))
plot3d(p1.hc, h=1)
```


You can enable figure captions by `fig_caption: yes` in YAML:

    output:
      rmarkdown::html_vignette:
        fig_caption: yes

Then you can use the chunk option `fig.cap = "Your figure caption."` in **knitr**.
